---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# detectduplicate

<!-- badges: start -->
<!-- badges: end -->

`detectduplicate` detects duplicate sequences of numbers. 
It can also detect pairs of sequences that have a constant offset, and/or a constant multiplier.

`detectduplicate` can be installed with 

```{r install, eval = FALSE}
# install.packages("pak")
pak::pak("richardjtelford/detectduplicate")
```


`detectduplicate` requires a vector of numbers as input. 

```{r example}
library(detectduplicate)
data("kp2014") # part of the data from Keiser & Pruitt 2014
dup_find_all(vec = kp2014$`Theridion murarium Aggressiveness...4`, type = "offset")
```

The result give the position and values of the first and second sets of duplicated values and any offset.

If data in several columns need to be checked, they should be appended into one vector.

```{r example2}
dup_find_all(
  vec = c(
    kp2014$`Theridion murarium Aggressiveness...4`,
    kp2014$`Theridion murarium Aggressiveness...5`,
    kp2014$`Theridion murarium Aggressiveness...6`
  ),
  type = "offset"
)
```
To see the duplicate sequences in situ, use `dup_show`.

```{r, eval = FALSE}
dup_show(kp2014, meta_cols = 1:3, test_cols = starts_with("Theridion"))
```


## Notes

`detectduplicate` will report the all the duplicate sequences it can find.

`detectduplicate` will not report sequences of identical values as duplicates. 
I don't think it is useful to report "duplicates" within and between long sequences of e.g. zeros.

`detectduplicate` reports duplicate values.
It does not report why. There may be valid reasons for duplicate sequences.

If very short sequences (e.g. length 3) are searched for, there is a high risk of false positives. 
This risk is especially high if the data are reported with low precision, 
cardinality is low, or test are made for pairs of sequences with a constant multiplier and offset 

If you find this package useful or have ideas about how it could be improve, 
please leave a message in the issues tab.

